Streaming CityJSON datasets

### 2024-04-23 paper/main.tex
Add conversion time as indication

@@

\begin{itemize}
  \item CityJSONSeq is an attractive alternative to CityJSON, in most uses it is better to use since it is compacter, processing it uses less memory and is faster.
  \item We have kept most of the structure of CityJSON so that parsers do not need to be adapted much.
  \item it opens up many possibilities for processing large 3dcm by using Unix pipes. A few of the tools developed for CityJSON are already reading/writing to stdin/stdout, so they can be chained together.
  \item cjseqview, cjseqval are two of them, but developing others to eg filter, calculate volumes or repair geometries would be trivial
  \item the nice part is that the tools do not need to be written in the same language, one pipeline can have tools built in Python and Rust and C++ and it all works nicely.
  \item extensions: these should be placed in the metadata or collection
\end{itemize}

Disadvantages:
\begin{itemize}
  \item     Software implementing CityJSON needs to account for both regular CityJSON and CityJSONSeq.
  \item  In case of many, small, interconnecting CityObjects, a global vertex list would provide better compression than the separate vertex lists of the CityJSONFeatures.
  \item  Appearances (esp. Material) are relatively heavy objects with many properties. If an appearance is shared across most CityObjects, duplicating it in each Feature could negate the effect of small vertex indices and actually increase the file size compared to a regular CityJSON file. This is just theorizing, haven't tested.
\end{itemize}

>>>>

It should be observe that the conversion is an efficient process: the rather large dataset (\textbf{Helskinki}, which contains more than \qty{77000} buildings and whose CityJSON file is \qty{572}{\mega\byte}) takes only \qty{4.7}{\sec} to be converted to a CityJSONSeq file, and the reverse operation takes \qty{5.7}{\sec} on a standard laptop.

@@

\begin{itemize}
  \item We have kept most of the structure of CityJSON so that parsers do not need to be adapted much.
  \item CityJSONSeq is an attractive alternative to CityJSON, in most uses it is better to use since it is compacter, processing it uses less memory and is faster.
  \item it opens up many possibilities for processing large 3dcm by using Unix pipes. A few of the tools developed for CityJSON are already reading/writing to stdin/stdout, so they can be chained together.
  \item cjseqview, cjseqval are two of them, but developing others to eg filter, calculate volumes or repair geometries would be trivial
  \item the nice part is that the tools do not need to be written in the same language, one pipeline can have tools built in Python and Rust and C++ and it all works nicely.
  \item extensions: these should be placed in the metadata or collection
\end{itemize}

Disadvantages:
\begin{itemize}
  \item  Software implementing CityJSON need to account for both regular CityJSON and CityJSONSeq.
  \item  In case of many, small, interconnecting CityObjects, a global vertex list would provide better compression than the separate vertex lists of the CityJSONFeatures.
  \item  Appearances (esp. Material) are relatively heavy objects with many properties. If an appearance is shared across most CityObjects, duplicating it in each Feature could negate the effect of small vertex indices and actually increase the file size compared to a regular CityJSON file. This is just theorizing, haven't tested.
\end{itemize}
